---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# statgenHTP

[![](https://www.r-pkg.org/badges/version/statgenHTP)](https://www.r-pkg.org/pkg/statgenHTP)
[![CRAN RStudio mirror downloads](https://cranlogs.r-pkg.org/badges/statgenHTP)](https://www.r-pkg.org/pkg/statgenHTP)
[![R-CMD-check](https://github.com/Biometris/statgenHTP/workflows/R-CMD-check/badge.svg)](https://github.com/Biometris/statgenHTP/actions?workflow=R-CMD-check)
[![codecov](https://codecov.io/gh/Biometris/statgenHTP/branch/master/graph/badge.svg)](https://app.codecov.io/gh/Biometris/statgenHTP)


**statgenHTP** is developed as an easy-to-use package for analyzing data coming 
from high throughput phenotyping (HTP) platform experiments. The package provides many options for plotting and exporting the results of the analyses. It was developed within the [EPPN^2020^ project](https://eppn2020.plant-phenotyping.eu/) to meet the needs for automated analyses of HTP data.

## Installation

* Install from CRAN:

```{r, eval = FALSE}
install.packages("statgenHTP")
```

* Install latest development version from GitHub (requires [remotes](https://github.com/r-lib/remotes) package):

```{r, eval = FALSE}
remotes::install_github("Biometris/statgenHTP", ref = "develop", dependencies = TRUE)
```
